---
title: 'Connectives and cognitive control: Data analysis and visualization'
author: ""
date: "2023-04-26"
output: html_document
---

# Set-up

Load required packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(eyetrackingR)
library(lme4)
library(readxl)
library(lmerTest)
library(data.table)
library(car)
library(gridExtra)
source("helpers.R")
theme_set(theme_bw())
palette = c("#d54700", "#56B4E9")
```

# Preparing data

## Eye-tracking data

Load eye-tracking data (make sure to unzip the .zip file if you haven't already):
```{r}
raw_eye_data = read.table('../data/conn_cog_control_timebin_1000sbefore.txt', sep = "\t", na.strings = ".", header = TRUE)
```

Prepare eye-tracking data:
```{r}
raw_eye_data$time_since_connective_onset = raw_eye_data$BIN_START_TIME - 1000
# change this if you generate timebin report starting at a point other than 1000s before connective onset

raw_eye_data$participant_number = raw_eye_data$RECORDING_SESSION_LABEL
raw_eye_data$list = as.numeric(raw_eye_data$list)
```

Fix labeling of so and but conditions:
```{r}
raw_eye_data = raw_eye_data %>% mutate(condition = case_when(
  condition == "alors" ~ "so",
  condition == "mais" ~ "but",
  condition == "training" ~ "training",
  TRUE ~ NA
),
condition_fr = case_when(
  condition == "so" ~ "alors",
  condition == "but" ~ "mais",
  condition == "training" ~ "training",
  TRUE ~ NA
))

raw_eye_data$condition = relevel(factor(raw_eye_data$condition), ref = 'but')
```

Correct a few errors in coding explicit selection choices (all were noted in comments while running the experiment):
```{r}
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 21032301 & raw_eye_data$TRIAL_LABEL == 'Trial: 9'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 21032304 & raw_eye_data$TRIAL_LABEL == 'Trial: 22'] = 0
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 03042307 & raw_eye_data$TRIAL_LABEL == 'Trial: 17'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 7042304 & raw_eye_data$TRIAL_LABEL == 'Trial: 23'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 11042306 & raw_eye_data$TRIAL_LABEL == 'Trial: 13'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 12042303 & raw_eye_data$TRIAL_LABEL == 'Trial: 19'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 17032305 & raw_eye_data$TRIAL_LABEL == 'Trial: 16'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 22032306 & raw_eye_data$TRIAL_LABEL == 'Trial: 1'] = 1
raw_eye_data$lex_related_image_selected[raw_eye_data$participant_number == 10042305 & raw_eye_data$TRIAL_LABEL == 'Trial: 1'] = 0
```


## Participant data

Load participant data:
```{r}
participant_df = read_excel('../data/participant-log-connectives-cog-control.xlsx')
participant_df = participant_df %>% type.convert(as.is = TRUE)
```

Rename age groups:
```{r}
participant_df = participant_df %>% mutate(age_group = case_when(
  age_group == '4' ~ '4-year-olds',
  age_group == '5' ~ '5-year-olds',
  age_group == '6' ~ '6-year-olds',
  age_group == 'adult' ~ 'adults'
), child_adult_group = case_when(
  child_adult_group == 'child' ~ 'children',
  child_adult_group == 'adult' ~ 'adults'
))
```

## Flanker data

Load Flanker data:
```{r}
flanker_files = list.files(path = '../data/flanker_data', full.names = TRUE)
flanker_df = plyr::ldply(flanker_files, read_csv)
flanker_df = flanker_df %>% type.convert()
flanker_df$participant_number_fl = flanker_df$subject
```


## Merging data

Merge eye-tracking data and participant data:
```{r}
raw_eye_data = left_join(raw_eye_data, participant_df)
raw_eye_data$lex_related_image_selected = as.numeric(raw_eye_data$lex_related_image_selected)
raw_eye_data$rt = as.numeric(raw_eye_data$rt)
```

Merge Flanker data and participant data:
```{r}
flanker_df = left_join(flanker_df, participant_df)
```

Take only children who completed novel word learning task:
```{r}
flanker_df = flanker_df %>% filter(!is.na(participant_number))
length(unique(flanker_df$participant_number_fl))
```

## Exclusions

Exclude participants who were distracted, bilingual, etc:
```{r}
eye_data = raw_eye_data %>% filter(exclude == "no")
```

Exclude participants who didn't complete more than half the trials:
```{r}
eye_data = eye_data %>% group_by(participant_number) %>% 
  mutate(total_trials_completed = max(TRIAL_INDEX)) %>%
  filter(total_trials_completed >= 12)
```

Exclude participants who didn't complete at least five so and five but trials:
```{r}
eye_data = eye_data %>% group_by(participant_number, condition) %>% 
  mutate(trials_completed_condition = length(unique(TRIAL_INDEX))) %>%
  group_by(participant_number) %>%
  filter((condition == 'so' & trials_completed_condition >=5) | 
           (condition == 'but' & trials_completed_condition >=5) |
           condition == 'training')
```

Check the number of participants in each age group:
```{r}
eye_data %>% group_by(participant_number) %>% filter(row_number() == 1) %>%
  group_by(age_group) %>% summarise(n = n())
```

Exclude the excluded participants from Flanker data too:
```{r}
flanker_df = flanker_df %>% filter(participant_number %in% eye_data$participant_number)
```

Write Flanker data to a separate file since we will calculate Flanker costs separately (no need to run this since file is already included):
```{r}
#write.csv(flanker_df, '../data/flanker_df.csv')
```

Flanker cost calculations are done in a separate script so load that data:
```{r}
full_flanker_df = read.csv('../data/full_flanker_df.csv')
```

Rename age groups in Flanker file:
```{r}
full_flanker_df = full_flanker_df %>% mutate(child_adult_group = case_when(
  child_adult_group == 'child' ~ 'children',
  child_adult_group == 'adult' ~ 'adults'
))
```

## Make eye-tracking data

Make eye-tracking data:
```{r}
eye_tr_df = make_eyetrackingr_data(eye_data, 
                       participant_column = 'RECORDING_SESSION_LABEL',
                       trial_column = 'trialnumber',
                       time_column = 'time_since_connective_onset', 
                       aoi_columns = c('AVERAGE_IA_1_SAMPLE_COUNT_.',
                                       'AVERAGE_IA_2_SAMPLE_COUNT_.'),
                       treat_non_aoi_looks_as_missing = TRUE,
                       trackloss_column = 'AVERAGE_OFF_SCREEN_SAMPLE_COUNT_.'
                       )
```

### Trackloss

Remove trackloss-ridden trials:
```{r}
trackloss_clean = trackloss_analysis(data = eye_tr_df)

eye_df_clean <- clean_by_trackloss(data = eye_tr_df, trial_prop_thresh = .25)
```

Assess mean trackloss per participant:
```{r}
trackloss_clean_partic <- unique(trackloss_clean[, c('RECORDING_SESSION_LABEL','TracklossForParticipant')])
```

Get mean and SD of proportion of samples contributed per trial:
```{r}
mean(1 - trackloss_clean_partic$TracklossForParticipant)
sd(1- trackloss_clean_partic$TracklossForParticipant)
```

# Novel word learning task

## Time course visualization

Pull out test trials:
```{r}
test_df = eye_df_clean %>% filter(practicestatus == "test")
test_df$condition = factor(test_df$condition)
```

Create columns for accuracy and selecting semantically associated image when child pointed to image on each trial:
```{r}
test_df = test_df %>% 
  mutate(correct_point = case_when(
  condition == 'so' & lex_related_image_selected == 1 ~ 'correct point',
  condition == 'but' & lex_related_image_selected == 0 ~ 'correct point',
  TRUE ~ 'incorrect point'
  ),
  lex_related_image_pointed = case_when(
  lex_related_image_selected == TRUE ~ 'Chose associated image',
  lex_related_image_selected == FALSE ~ 'Chose contrasting image'
  ))
```

### Age group

New label for age group, to make graphs look nicer:
```{r}
test_df = test_df %>% mutate(age_group_label = case_when(
  age_group == '4-year-olds' ~ 'a) 4-year-olds (n=24)',
  age_group == '5-year-olds' ~ 'b) 5-year-olds (n=23)',
  age_group == '6-year-olds' ~ 'c) 6-year-olds (n=24)',
  age_group == 'adults' ~ 'd) adults (n=24)',
))
```

Make time sequence data with age group as predictor:
```{r}
timecourse_age_group <- make_time_sequence_data(test_df, time_bin_size = 20, 
                                         predictor_columns = c("condition", "age_group_label"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")
```

Make time course graph by age group:
```{r}
plot(timecourse_age_group, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_wrap(~age_group_label, ncol=2) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by condition")

ggsave('timecourse_age_group_2by2.pdf', path = '../graphs', height = 5, width = 9)
```

### Children vs. adults

Make time sequence data with child/adult group as predictor:
```{r}
test_df2 = test_df %>% 
  mutate(child_adult_group = case_when(
    child_adult_group == "adults" ~ "adults (n = 24)",
    child_adult_group == "children" ~ "children ages 4 to 6 (n = 71)"
  ))

timecourse_child_adult_group <- make_time_sequence_data(test_df2, time_bin_size = 20, 
                                         predictor_columns = c("condition",
                                                               "child_adult_group"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")

```

Make time course graph for children vs. adults:
```{r}
plot(timecourse_child_adult_group, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_wrap(~child_adult_group, nrow = 2) +
  annotate("text", x=-150, y=.9, label="connective \nonset", size = 2.5) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by condition")

ggsave('timecourse_child_adult.pdf', path = '../graphs', height = 5, width = 7)
```

### Correct vs. incorrect points

Make time sequence data with child/adult group and correct/incorrect point as predictors:
```{r}
timecourse_pointing_correct_child_adult <- make_time_sequence_data(test_df2, 
                                                                   time_bin_size = 20, 
                                         predictor_columns = c("condition",
                                                               "child_adult_group",
                                                               "correct_point"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")
```

Make time course graph for children vs. adults and correct vs. incorrect points:
```{r}
plot(timecourse_pointing_correct_child_adult, predictor_column = "condition") + 
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  scale_fill_manual(name = 'Condition', values = palette) +
  scale_color_manual(name = 'Condition', values = palette) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_grid(rows = vars(correct_point), cols = vars(child_adult_group)) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("")

ggsave('timecourse_pointing_child_adult.pdf', path = '../graphs', height = 5, width = 9)
ggsave('timecourse_pointing_child_adult.jpg', path = '../graphs', height = 5, width = 9)
```

### Item effects

Make time sequence data with child/adult group and item as predictors:
```{r}
timecourse_item_child = test_df %>% filter(child_adult_group == 'children') %>%
  make_time_sequence_data(time_bin_size = 20, 
                                         predictor_columns = c("condition",
                                                               "novelword"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")
```

Make time course graph for items:
```{r}
plot(timecourse_item_child, predictor_column = "condition") + 
  theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_wrap(~novelword, nrow = 4, ncol = 5) +
  #facet_grid(rows = vars(novelword), cols = vars(child_adult_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by item")

ggsave('timecourse_item_child.pdf', path = '../graphs', height = 7, width = 9)
```

### Annotated time course graphs

Create data frame with info for annotated versions of time course graphs (this comes from cluster analyses, which are in next section):
```{r}
time_clust_audio_age_group = data.frame(
  age_group_label = c('a) 4-year-olds (n=24)', 'b) 5-year-olds (n=23)', 'c) 6-year-olds (n=24)', 'd) adults (n=24)', 'a) 4-year-olds (n=24)', 'b) 5-year-olds (n=23)', 'c) 6-year-olds (n=24)', 'd) adults (n=24)'),
  p_val = c('p < 0.05', 'p < 0.01', 'p = 0.11', 'p < 0.01', 'p < 0.05', 'p < 0.01', 'p = 0.11', 'p < 0.01'),
  time_clust_start = c(1240, 740, 1060, 460, 1240, 740, 1060, 460),
  condition = c('so', 'so', 'so', 'so', 'but', 'but', 'but', 'but')
)

time_clust_audio_child_adult = data.frame(
  child_adult_group = c('children ages 4 to 6 (n = 71)', 'children ages 4 to 6 (n = 71)', 'adults (n = 24)', 'adults (n = 24)'),
  p_val = c('p < 0.01***', 'p < 0.01***', 'p < 0.01***', 'p < 0.01***'),
  time_clust_start = c(900, 900, 460, 460),
  time_clust_end = c(2100, 2100, 4120, 4120),
  condition = c('so', 'so', 'but', 'but')
)
```

Annotated version of time course graph by age group:
```{r}
plot(timecourse_age_group, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_wrap(~age_group_label, ncol=1) +
  geom_rect(data = timecourse_age_group[1,], aes(xmin = 1240, xmax = 2020, ymin = -Inf, ymax = Inf), alpha = 0.12, color = NA, fill = 'darkorange') +
  geom_rect(data = timecourse_age_group[26682,], aes(xmin = 740, xmax = 2060, ymin = -Inf, ymax = Inf), alpha = 0.12, color = NA, fill = 'darkorange') +
  geom_rect(data = timecourse_age_group[1176,], aes(xmin = 1060, xmax = 1580, ymin = -Inf, ymax = Inf), alpha = 0.13, color = NA, fill = 'gold2') +
  geom_rect(data = timecourse_age_group[12437,], aes(xmin = 460, xmax = 4000, ymin = -Inf, ymax = Inf), alpha = 0.12, color = NA, fill = 'darkorange') +
  annotate('rect', xmin = -1000, xmax = -10, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = -500, y = 0.15, label = 'Emilie had soup for lunch,', size = 2) +
  annotate('rect', xmin = 10, xmax = 222, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 110, y = 0.15, label = 'so/\nbut', size = 2) +
  annotate('rect', xmin = 230, xmax = 1298, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 750, y = 0.15, label = 'she used a mora', size = 2) +
  annotate('rect', xmin = 2458, xmax = 3645, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 3060, y = 0.15, label = 'Can you show me a mora?', size = 2) +
  geom_text(data = time_clust_audio_age_group, aes(x = time_clust_start + 270, y = .9, label = p_val), color = 'black', size = 3) +
  scale_fill_manual(name = 'Condition', values = palette) +
  scale_color_manual(name = 'Condition', values = palette) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("")

ggsave('timecourse_age_group_annotated.pdf', path = '../graphs', height = 7, width = 7)
ggsave('timecourse_age_group_annotated.jpg', path = '../graphs', height = 7, width = 7)
```

Make annotated version of time course graph for children vs. adults:
```{r}
plot(timecourse_child_adult_group, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_wrap(~child_adult_group, ncol=1) +
  geom_rect(data = timecourse_child_adult_group[1,], aes(xmin = 900, xmax = 2100, ymin = -Inf, ymax = Inf), alpha = 0.12, color = NA, fill = 'darkorange') +
    geom_rect(data = timecourse_child_adult_group[20634,], aes(xmin = 460, xmax = 4000, ymin = -Inf, ymax = Inf), alpha = 0.12, color = NA, fill = 'darkorange') +
  annotate('rect', xmin = -999, xmax = -10, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = -500, y = 0.15, label = 'Emilie had soup for lunch,', size = 2.5) +
  annotate('rect', xmin = 10, xmax = 222, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 110, y = 0.15, label = 'so/\nbut', size = 2.5) +
  annotate('rect', xmin = 230, xmax = 1298, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 750, y = 0.15, label = 'she used a mora', size = 2.5) +
  annotate('rect', xmin = 2458, xmax = 3645, ymin = 0.05, ymax = 0.25, alpha = 0.3, 
           color = 'darkgray', fill = 'darkgray') +
  annotate('text', x = 3060, y = 0.15, label = 'Can you show me a mora?', size = 2.5) +
  geom_text(data = time_clust_audio_child_adult, aes(x = 1400, y = .9, label = p_val), color = 'black', size = 3) +
  scale_fill_discrete(name = 'Condition') +
  scale_color_discrete(name = 'Condition') +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by condition")

ggsave('timecourse_child_adult_annotated.pdf', path = '../graphs', height = 6, width = 8)
```


## Cluster analysis

### Children vs. adults

Separate time course data into children vs. adults:
```{r}
timecourse_child = test_df %>%
  filter(child_adult_group == "children") %>%
  make_time_sequence_data(time_bin_size = 20, predictor_column = "condition",
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")

timecourse_adult = test_df %>% 
  filter(child_adult_group == "adults") %>%
  make_time_sequence_data(time_bin_size = 20, predictor_column = "condition",
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number")
```

Make time cluster data for children:
```{r}
timeclust_child = make_time_cluster_data(timecourse_child,
                                      test = "t.test", paired = TRUE,
                                      predictor_column = "condition",
                                      aoi = "AVERAGE_IA_1_SAMPLE_COUNT_.",
                                      threshold = 1.5,
                                      formula = ArcSin ~ condition)
```

Plot time cluster data for children:
```{r}
plot(timeclust_child, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) + 
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE) +
  geom_vline(xintercept=0, colour="black",size=I(1.5),show.legend = FALSE) +
  xlab("Time since connective onset (ms)") +
  ylab("Cluster T test statistic") +
  ggtitle("Cluster sum statistic for difference in looks to semantically associated\n image by condition: Children")

ggsave('timecluster_children.pdf', path = '../graphs', height = 4, width = 6)
```

Carry out time cluster analysis for children (note: this code takes a while to run, so budget at least 5-10 minutes):
```{r}
timeclust_analysis_child = analyze_time_clusters(timeclust_child, within_subj = TRUE, paired = TRUE, samples = 1000, parallel = TRUE, shuffle_by = c("condition"))
summary(timeclust_analysis_child)
```

Plot time cluster analysis for children:
```{r}
plot(timeclust_analysis_child, type = 'estimate') + theme_bw() +
    ggtitle("Cluster sum statistic for difference in looks to semantically \nassociated image by condition: Children")

ggsave('timecluster_analysis_child.pdf', path = '../graphs', height = 4, width = 6)
```

For children, there is a sig. cluster between 900 and 2100 ms (p < 0.01).

Note: if you do this for individual child age groups (code below), there are clusters at:
1240 to 2020 for 4-year-olds (p = 0.049)
740 to 2060 for 5-year-olds (p = 0.000)
1060 to 1580 for 6-year-olds (p = 0.11)

Make time cluster data for adults:
```{r}
timeclust_adult = make_time_cluster_data(timecourse_adult,
                                      test= "t.test", paired = TRUE,
                                      predictor_column = "condition",
                                      aoi = "AVERAGE_IA_1_SAMPLE_COUNT_.",
                                      threshold = 1.5,
                                      formula = ArcSin ~ condition)
```

Plot time cluster data for adults:
```{r}
plot(timeclust_adult, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) + 
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE) +
  geom_vline(xintercept=0, colour="black",size=I(1.5),show.legend = FALSE) +
  xlab("Time since connective onset (ms)") +
  ylab("Cluster T test statistic") +
  ggtitle("T test statistic for difference in looks to semantically associated\n image by condition: Adults")

ggsave('timecluster_adult.pdf', path = '../graphs', height = 4, width = 6)
```

Carry out time cluster analysis for adults:
```{r}
timeclust_analysis_adult = analyze_time_clusters(timeclust_adult, within_subj = TRUE, paired = TRUE, samples = 1000, parallel = TRUE, shuffle_by = "condition")
summary(timeclust_analysis_adult)
```

Plot time cluster analysis for adults:
```{r}
plot(timeclust_analysis_adult, type = 'estimate') + theme_bw() +
    ggtitle("Cluster sum statistic for difference in looks to semantically \nassociated image by condition: Adults")

ggsave('timecluster_analysis_adult.pdf', path = '../graphs', height = 4, width = 6)
```

For adults, there is a sig. cluster between 460 and 4120 ms (p < 0.001).

### Child age groups

Make time cluster data for each child age group:
```{r}
timecourse_child4 = timecourse_child %>% filter(age_group == '4-year-olds')
timecourse_child5 = timecourse_child %>% filter(age_group == '5-year-olds')
timecourse_child6 = timecourse_child %>% filter(age_group == '6-year-olds')

timeclust_child4 = make_time_cluster_data(timecourse_child4,
                                      test = "t.test", paired = TRUE,
                                      predictor_column = "condition",
                                      aoi = "AVERAGE_IA_1_SAMPLE_COUNT_.",
                                      threshold = 1.5,
                                      formula = ArcSin ~ condition)
timeclust_child5 = make_time_cluster_data(timecourse_child5,
                                      test = "t.test", paired = TRUE,
                                      predictor_column = "condition",
                                      aoi = "AVERAGE_IA_1_SAMPLE_COUNT_.",
                                      threshold = 1.5,
                                      formula = ArcSin ~ condition)
timeclust_child6 = make_time_cluster_data(timecourse_child6,
                                      test = "t.test", paired = TRUE,
                                      predictor_column = "condition",
                                      aoi = "AVERAGE_IA_1_SAMPLE_COUNT_.",
                                      threshold = 1.5,
                                      formula = ArcSin ~ condition)
```

Carry out time cluster analysis for children (note: this code takes a while to run, so budget at least 5-10 minutes for each age group):
```{r}
timeclust_analysis_child4 = analyze_time_clusters(timeclust_child4, within_subj = TRUE, paired = TRUE, samples = 1000, parallel = TRUE, shuffle_by = c("condition"))
summary(timeclust_analysis_child4)

timeclust_analysis_child5 = analyze_time_clusters(timeclust_child5, within_subj = TRUE, paired = TRUE, samples = 1000, parallel = TRUE, shuffle_by = c("condition"))
summary(timeclust_analysis_child4)

timeclust_analysis_child6 = analyze_time_clusters(timeclust_child6, within_subj = TRUE, paired = TRUE, samples = 1000, parallel = TRUE, shuffle_by = c("condition"))
summary(timeclust_analysis_child4)
```

## Pointing data

Create dataframe with one row per trial per participant and calculate participant's proportion of trials per condition with semantically associated image selected:
```{r}
test_df_trial = test_df %>% group_by(participant_number, TRIAL_LABEL) %>%
  filter(row_number() == 1) %>%
  group_by(participant_number, condition) %>%
  mutate(partic_cond_trial_num = n(),
         partic_prop_lex_related_image_selected =
           mean(na.omit(lex_related_image_selected)))
```

Create data frame with one row per participant per condition:
```{r}
test_df_partic_cond = test_df_trial %>% group_by(participant_number, condition) %>%
  filter(row_number() == 1)
```

### Age group

Summarize number of trials on each condition for which participants selected the semantically associated image:
```{r}
pointing_summ = test_df_partic_cond %>%
  group_by(condition, age_group) %>%
  summarise(n = n(), 
            mean_prop_lex_related_image_selected =
              mean(partic_prop_lex_related_image_selected),
            CI.low = ci.low(partic_prop_lex_related_image_selected),
            CI.high = ci.high(partic_prop_lex_related_image_selected)) %>%
  mutate(YMin = mean_prop_lex_related_image_selected - CI.low, 
         YMax = mean_prop_lex_related_image_selected + CI.high)
```

Graph proportion of trials on each condition for which participants selected the semantically associated image, by age group:
```{r}
ggplot(pointing_summ) +
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  aes(x = condition, y = mean_prop_lex_related_image_selected, fill = condition) +
  facet_wrap(~age_group) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) + 
  geom_jitter(data = test_df_partic_cond, aes(x = condition, y = partic_prop_lex_related_image_selected), 
              shape = 21, size = 1, width = 0.2, height = 0, stroke = 0.4, alpha = 0.3) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0, position = position_dodge(.9)) +
  scale_fill_discrete(name = "Condition") +
  scale_y_continuous(limits = c(0, 1.06), oob = scales::squish) +
  ggtitle("Prop. of trials with semantically associated image selected by condition") +
  xlab("Condition") +
  ylab("Prop. of trials with semantically associated image selected")

ggsave('pointing_age_group_bar.pdf', path = '../graphs', height = 4, width = 6)
```

Line graph of proportion of trials on each condition for which participants selected the lexically related image, by age group:
```{r}
ggplot(pointing_summ) +
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  aes(x = age_group, y = mean_prop_lex_related_image_selected, group = condition, color = condition) +
  geom_point(data = test_df_partic_cond, aes(x = age_group, y = partic_prop_lex_related_image_selected, group = condition), 
              position = position_jitterdodge(dodge.width=.3, jitter.width = .2), shape = 21, size = 1, stroke = 0.4, alpha = 0.8) +
  geom_line(position=position_dodge(width=0.3)) + 
  geom_point(position=position_dodge(width=0.3), size = 2.5) +
  ylim(0,1.05) +
  geom_hline(yintercept=0.5, colour="black",linetype = 3, size=I(1),show.legend = FALSE)+
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = .2, position=position_dodge(width=0.3)) +
  scale_color_manual(name = "Condition", values = palette) +
  xlab("Age group") +
  ylab("Prop. selections of semantically associated image") +
  ggtitle("") 

ggsave('pointing_age_group_line.pdf', path = '../graphs', height = 4, width = 6)
ggsave('pointing_age_group_line.jpg', path = '../graphs', height = 4, width = 6)
```

### Children vs. adults

```{r}
test_df_partic_cond = test_df_partic_cond %>% 
  mutate(child_adult_group_label = case_when(
    child_adult_group == 'adults' ~ 'adults (n = 24)',
    child_adult_group == 'children' ~ 'children ages 4 to 6 (n = 71)'))
```


Summarize number of trials on each condition for which participants selected the semantically associated image (for children vs. adults):
```{r}
pointing_summ_child_adult = test_df_partic_cond %>%
  group_by(condition, child_adult_group_label) %>%
  summarise(n = n(), 
            mean_prop_lex_related_image_selected =
              mean(partic_prop_lex_related_image_selected),
            CI.low = ci.low(partic_prop_lex_related_image_selected),
            CI.high = ci.high(partic_prop_lex_related_image_selected)) %>%
  mutate(YMin = mean_prop_lex_related_image_selected - CI.low, 
         YMax = mean_prop_lex_related_image_selected + CI.high)
```

Graph proportion of trials on each condition for which participants selected the semantically associated image, for children vs. adults:
```{r}
ggplot(pointing_summ_child_adult) +
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  aes(x = condition, y = mean_prop_lex_related_image_selected, fill = condition) +
  facet_wrap(~child_adult_group_label) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) + 
  geom_jitter(data = test_df_partic_cond, aes(x = condition, y = partic_prop_lex_related_image_selected), 
              shape = 21, size = 1, width = 0.2, height = 0, stroke = 0.4, alpha = 0.3) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0, position = position_dodge(.9)) +
  scale_fill_discrete(name = "Condition") +
  scale_y_continuous(limits = c(0, 1.06), oob = scales::squish) +
  ggtitle("Prop. of trials with semantically associated image selected by condition") +
  xlab("Condition") +
  ylab("Prop. semantically associated image selected")

ggsave('pointing_child_adult_group_bar.pdf', path = '../graphs', height = 4, width = 6)
```

### Item

Summarize by-item proportion of selecting the semantically associated image (for children vs. adults):
```{r}
item_summ_child_adult = test_df_trial %>%
  group_by(condition, child_adult_group, novelword) %>%
  summarise(n = n(), 
            mean_prop_lex_related_image_selected =
              mean(partic_prop_lex_related_image_selected),
            CI.low = ci.low(partic_prop_lex_related_image_selected),
            CI.high = ci.high(partic_prop_lex_related_image_selected)) %>%
  mutate(YMin = mean_prop_lex_related_image_selected - CI.low, 
         YMax = mean_prop_lex_related_image_selected + CI.high)
```

Graph proportion of trials on each condition for each item for which participants selected the semantically associated image:
```{r}
ggplot(item_summ_child_adult) +
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  aes(x = novelword, y = mean_prop_lex_related_image_selected, fill = condition) +
  facet_grid(cols = vars(child_adult_group), rows = vars(condition)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) + 
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0, position = position_dodge(.9)) +
  scale_fill_discrete(name = "Condition") +
  scale_y_continuous(limits = c(0, 1.06), oob = scales::squish) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Prop. of trials with semantically associated image selected by item") +
  xlab("Novel word") +
  ylab("Prop. of trials with semantically associated image selected")

ggsave('pointing_item_child_adult.pdf', path = '../graphs', height = 4, width = 8)
```

# Novel word learning task analysis

## Pointing data

Test whether condition predicts pointing to semantically associated image for children:
```{r}
pointing_lm_child = lmer(lex_related_image_selected ~ condition +
                     (1|participant_number) + (1|novelword), 
                   data = test_df_trial, subset = child_adult_group == 'children')
summary(pointing_lm_child)
```

Test whether condition predicts pointing to semantically associated image for adults:
```{r}
pointing_lm_adult = lmer(lex_related_image_selected ~ condition +
                     (1|participant_number) + (1|novelword), 
                   data = test_df_trial, subset = age_group == 'adults')
summary(pointing_lm_adult)
```

Test whether age predicts points to semantically associated image (post-hoc):
```{r}
pointing_lm_age = lmer(lex_related_image_selected ~ condition*age_months +
                     (1|participant_number) + (1|novelword), 
                   data = test_df_trial, subset = (child_adult_group == 'children'))
summary(pointing_lm_age)
```

## Proportion of looks

Pull out looking data during window where there was a significant time cluster for children (change start time to 0 and end time to 4000 if you want to examine full window after connective onset):
```{r}
window_test_df = subset_by_window(test_df, 
                                  window_start_time = 900, 
                                  window_end_time = 2100)

# change start time to 0 and end time to 4000 if you want to examine full window after connective onset
```

Calculate each participant's mean proportion of looks to the semantically associated image in each condition:
```{r}
window_test_df_partic = make_time_window_data(window_test_df, 
                                              aois = 'AVERAGE_IA_1_SAMPLE_COUNT_.',
                                              predictor_columns = c("condition", "age_group",
                                                                    "child_adult_group"), 
                                              summarize_by = "participant_number")
```

Calculate each participant's proportion of looks to the semantically associated image in each trial:
```{r}
window_test_df_partic_trial = make_time_window_data(window_test_df, 
                                              aois = 'AVERAGE_IA_1_SAMPLE_COUNT_.',
                                              predictor_columns = c("condition",
                                                                    "age_group",
                                                                "child_adult_group",
                                                                "trialnumber"), 
                                              summarize_by = "participant_number")
```


### Age group

Plot raw prop. looking data by age group:
```{r}
plot(window_test_df_partic, predictor_columns = c("condition"), dv = "Prop") + 
  theme_bw() +
  theme(text = element_text(size = 12)) +  
  facet_wrap(~age_group) +
  ylim(0,1) +
  xlab("Condition") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by condition")

ggsave('prop_looks_age_group.pdf', path = '../graphs', height = 6, width = 8)
```

### Children vs. adults

Plot raw prop looking data for children vs. adults:
```{r}
plot(window_test_df_partic, predictor_columns = c("condition"), dv = "Prop") + 
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  facet_wrap(~child_adult_group) +
  ylim(0,1) +
  xlab("Condition") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image by condition")

ggsave('prop_looks_child_adult_group.pdf', path = '../graphs', height = 4, width = 6)
```

### Test for difference in proportion of looks by condition

Pull out just ArcSin-transformed prop of looks for adults and children:
```{r}
prop_looks_partic_child = window_test_df_partic %>% select(participant_number, condition, age_group, child_adult_group, ArcSin) %>% filter(child_adult_group == 'children') %>%
  spread(key = 'condition', value = 'ArcSin') %>%
  rename(arcsin_prop_looks_but = but, arcsin_prop_looks_so = so)

prop_looks_partic_adult = window_test_df_partic %>% select(participant_number, condition, age_group, child_adult_group, ArcSin) %>% filter(child_adult_group == 'adults') %>%
  spread(key = 'condition', value = 'ArcSin') %>%
  rename(arcsin_prop_looks_but = but, arcsin_prop_looks_so = so)
```

T test to see if there is a significant difference in proportion of looks to semantically associated image by condition for children and adults:
```{r}
t.test(prop_looks_partic_child$arcsin_prop_looks_so, prop_looks_partic_child$arcsin_prop_looks_but, paired = TRUE)

t.test(prop_looks_partic_adult$arcsin_prop_looks_so, prop_looks_partic_adult$arcsin_prop_looks_but, paired = TRUE)
```

Run a model to test for an effect of condition, for children and adults:
```{r}
prop_looks_lm_children = lmer(ArcSin ~ condition + (1|participant_number) +
                        (1|novelword), data = window_test_df_item,
                      subset = child_adult_group == 'children')
summary(prop_looks_lm_children)

prop_looks_lm_adults = lmer(ArcSin ~ condition + (1|participant_number) +
                        (1|novelword), data = window_test_df_item,
                      subset = child_adult_group == 'adults')
summary(prop_looks_lm_adults)
```

Both children and adults looked significantly more at the semantically associated image in the so condition than in the but condition.

### Item

Make a version of data with item effects:
```{r}
window_test_df_item = make_time_window_data(window_test_df, 
                                              aois = 'AVERAGE_IA_1_SAMPLE_COUNT_.',
                                              predictor_columns = c("condition", "novelword",
                                                                    "child_adult_group"), 
                                              summarize_by = "participant_number")
```

Summarize by item:
```{r}
prop_looks_item_summ = window_test_df_item %>% 
  group_by(child_adult_group, condition, novelword) %>% 
  summarise(n = n(), 
            mean_prop_looks_lex_related_image =
              mean(Prop),
            CI.low = ci.low(Prop),
            CI.high = ci.high(Prop)) %>%
  mutate(YMin = mean_prop_looks_lex_related_image - CI.low, 
         YMax = mean_prop_looks_lex_related_image + CI.high)
```

Plot item effects on proportion of looks:
```{r}
ggplot(prop_looks_item_summ) +
  theme_bw() +
  theme(text = element_text(size = 10)) +  
  aes(x = novelword, y = mean_prop_looks_lex_related_image, fill = condition) +
  facet_grid(cols = vars(child_adult_group), rows = vars(condition)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) + 
  geom_errorbar(aes(ymin = YMin, ymax = YMax), width = 0, position = position_dodge(.9)) +
  scale_fill_discrete(name = "Condition") +
  scale_y_continuous(limits = c(0, 1.06), oob = scales::squish) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  ggtitle("Prop. of looks to semantically associated image by item") +
  xlab("Novel word") +
  ylab("Prop. of looks at semantically associated image")

ggsave('prop_looks_item_child_adult.pdf', path = '../graphs', height = 4, width = 8)
```

### Interaction with age

Analysis to see if there's an interaction of condition and age (post-hoc:
```{r}
window_test_df_item_agegroup = make_time_window_data(window_test_df, 
                                              aois = 'AVERAGE_IA_1_SAMPLE_COUNT_.',
                                              predictor_columns = c("condition", "novelword",
                                                                    "age_group"), 
                                              summarize_by = "participant_number")

window_test_df_item_agegroup = window_test_df_item_agegroup %>% mutate(age_group_relevel = factor(age_group, levels = c('5-year-olds', '4-year-olds', '6-year-olds', 'adults')))

looks_cond_age = lmer(ArcSin ~ condition*age_group_relevel + (1|novelword) +
                        (1|participant_number), data = window_test_df_item_agegroup,
                      subset = age_group != 'adults')
summary(looks_cond_age)
```

### Looks to correct image

Make a version of data with CORRECT looks on so and but trials:
```{r}
window_test_df_partic_cond_correct = make_time_window_data(window_test_df, 
                                              aois = c('AVERAGE_IA_1_SAMPLE_COUNT_.',
                                                       'AVERAGE_IA_2_SAMPLE_COUNT_.'),
                                              predictor_columns = c("condition", "age_group", "child_adult_group"), 
                                              summarize_by = "participant_number")
```

Pull out only prop of looks to CORRECT image:
```{r}
window_test_df_partic_cond_correct = window_test_df_partic_cond_correct %>% 
  filter((condition == 'so' & AOI == 'AVERAGE_IA_1_SAMPLE_COUNT_.') |
           (condition == 'but' & AOI == 'AVERAGE_IA_2_SAMPLE_COUNT_.'))
```

Pull out just raw prop of looks to correct image for adults and children (we will use this for the relationship to Flanker data later):
```{r}
prop_looks_correct_child = window_test_df_partic_cond_correct %>% 
  select(participant_number, condition, age_group, child_adult_group, Prop) %>%
  filter(child_adult_group == 'children') %>%
  spread(key = 'condition', value = 'Prop') %>%
  rename(prop_correct_looks_but = but, prop_correct_looks_so = so)

prop_looks_correct_adults = window_test_df_partic_cond_correct %>% 
  select(participant_number, condition, age_group, child_adult_group, Prop) %>%
  filter(child_adult_group == 'adults') %>%
  spread(key = 'condition', value = 'Prop') %>%
  rename(prop_correct_looks_but = but, prop_correct_looks_so = so)
```

# Relationship of Flanker performance and pointing performance

Create a column for accuracy on pointing trials:
```{r}
pointing_df_partic_cond = test_df_partic_cond %>% 
  mutate(partic_prop_correct_points = case_when(
  condition == 'so' ~ partic_prop_lex_related_image_selected,
  condition == 'but' ~ (1 - partic_prop_lex_related_image_selected)))
```

We will only be analyzing children, as adults did not complete the Flanker task:
```{r}
pointing_df_partic_cond = pointing_df_partic_cond %>% 
  filter(child_adult_group == 'children')
```

Calculate participants' proportion of correct points on so and but trials:
```{r}
pointing_df_partic_cond = pointing_df_partic_cond %>% 
  group_by(participant_number, condition) %>%
  summarise(partic_prop_correct_points = partic_prop_correct_points,
            participant_number_fl = participant_number_fl,
            age_group = age_group,
            age_months = age_months)
```

Reshape to create dataframe with one row per participant:
```{r}
pointing_df_partic_cond = pointing_df_partic_cond %>% 
  spread(key = 'condition', value = 'partic_prop_correct_points') %>%
  rename(prop_correct_points_but = but, prop_correct_points_so = so)
```

Merge with Flanker data:
```{r}
pointing_df_partic_cond = right_join(pointing_df_partic_cond, full_flanker_df)
```

Change proportion correct points for but to z-scores:
```{r}
pointing_df_partic_cond$mean_prop_correct_points_but = mean(pointing_df_partic_cond$prop_correct_points_but)
pointing_df_partic_cond$sd_prop_correct_points_but = sd(pointing_df_partic_cond$prop_correct_points_but)

pointing_df_partic_cond = pointing_df_partic_cond %>% 
  mutate(prop_correct_points_but_z_score = ((prop_correct_points_but - mean_prop_correct_points_but)/sd_prop_correct_points_but))
```

Change proportion correct points for so to z-scores:
```{r}
pointing_df_partic_cond$mean_prop_correct_points_so = mean(pointing_df_partic_cond$prop_correct_points_so)
pointing_df_partic_cond$sd_prop_correct_points_so = sd(pointing_df_partic_cond$prop_correct_points_so)

pointing_df_partic_cond = pointing_df_partic_cond %>% 
  mutate(prop_correct_points_so_z_score = ((prop_correct_points_so - mean_prop_correct_points_so)/sd_prop_correct_points_so))
```

## Pointing and Flanker costs

Run a regression to test whether Flanker performance predicts performance on but trials (pointing):
```{r}
fl_pointing_lm = lm(prop_correct_points_but_z_score ~ composite_congruency_effect + composite_switch_effect + flanker_nogo_effect_z_score + age_months_z_score + prop_correct_points_so_z_score, 
                    data = pointing_df_partic_cond)
summary(fl_pointing_lm)

vif(fl_pointing_lm)
```

Run it without combining RT and acc z-scores:
```{r}
fl_pointing_separate_lm = lm(prop_correct_points_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score +  flanker_nogo_effect_z_score + age_months_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond)
summary(fl_pointing_separate_lm)

vif(fl_pointing_separate_lm)
```

### Plot relationship between Flanker Switch RT cost and correct points on but trials

To plot relationship between Flanker switch cost RT and points to correct image on but trials, create versions of the regression predicting each outcome and get the residuals:
```{r}
fl_pointing_switch_rt = lm(flanker_switch_rt_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_acc_z_score +  flanker_nogo_effect_z_score + age_months_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond)
switch_resid = residuals.lm(fl_pointing_switch_rt)

fl_pointing_correct_points_but = lm(prop_correct_points_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_acc_z_score +  flanker_nogo_effect_z_score + age_months_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond)
correct_points_but_resid = residuals.lm(fl_pointing_correct_points_but)

switch_but_resid = data.frame(switch_resid, correct_points_but_resid)
```

Plot these residuals to get the relationship between switch RT cost and correct points on but trials:
```{r}
ggplot(data = switch_but_resid, aes(x = switch_resid, y = correct_points_but_resid)) +
  theme(text = element_text(size = 14)) +  
  geom_point() +
  geom_smooth(method="lm") +
  xlab('Flanker Switch reaction time cost') +
  ylab('Prop. points to correct image on but trials') +
  ggtitle("'But' accuracy and Flanker Switch reaction time cost") 

ggsave('resid_switch_correct_but_points.pdf', path = '../graphs', height = 4, width =6)
```

## Relationship of Flanker performance and looking to correct image

Merge Flanker data and proportion of looks data:
```{r}
prop_looks_correct_fl = right_join(prop_looks_correct_child, full_flanker_df, by = c('participant_number'))
```

Calculate z-score for proportion of looks to correct image on so trials:
```{r}
prop_looks_correct_fl$mean_prop_correct_looks_so = mean(prop_looks_correct_fl$prop_correct_looks_so)
prop_looks_correct_fl$sd_prop_correct_looks_so = sd(prop_looks_correct_fl$prop_correct_looks_so)

prop_looks_correct_fl = prop_looks_correct_fl %>% 
  mutate(prop_correct_looks_so_z_score = ((prop_correct_looks_so - mean_prop_correct_looks_so)/sd_prop_correct_looks_so))
```

Calculate z-score for proportion of looks to correct image on but trials:
```{r}
prop_looks_correct_fl$mean_prop_correct_looks_but = mean(prop_looks_correct_fl$prop_correct_looks_but)
prop_looks_correct_fl$sd_prop_correct_looks_but = sd(prop_looks_correct_fl$prop_correct_looks_but)

prop_looks_correct_fl = prop_looks_correct_fl %>% 
  mutate(prop_correct_looks_but_z_score = ((prop_correct_looks_but - mean_prop_correct_looks_but)/sd_prop_correct_looks_but))
```

### Prop looks and Flanker costs

Run a regression to test whether Flanker performance predicts looking performance on but trials:
```{r}
fl_looking_lm = lm(prop_correct_looks_but_z_score ~ composite_congruency_effect + composite_switch_effect + flanker_nogo_effect_z_score + age_months_z_score + prop_correct_looks_so_z_score, data = prop_looks_correct_fl)
summary(fl_looking_lm)

vif(fl_looking_lm)
```

Run it without combining RT and acc z-scores:
```{r}
fl_looking_separate_lm = lm(prop_correct_looks_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score +  flanker_nogo_effect_z_score + age_months_z_score + prop_correct_looks_so_z_score, data = prop_looks_correct_fl)
summary(fl_looking_separate_lm)
vif(fl_looking_separate_lm)
```

### Plot relationship between Flanker no go cost and correct looks on but trials

To plot relationship between Flanker no go cost and looks to correct image on but trials, create versions of the regression predicting each outcome and get the residuals:
```{r}
fl_looking_nogo = lm(flanker_nogo_effect_z_score ~ composite_congruency_effect + composite_switch_effect + age_months_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl)
nogo_resid = residuals.lm(fl_looking_nogo)

fl_looking_correct_looks_but = lm(prop_correct_looks_but_z_score ~ composite_congruency_effect + composite_switch_effect + age_months_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl)
correct_looks_but_resid = residuals.lm(fl_looking_correct_looks_but)

nogo_but_resid = data.frame(nogo_resid, correct_looks_but_resid)

fl_looking_nogo = lm(flanker_nogo_effect_z_score ~ composite_congruency_effect + composite_switch_effect + age_months_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl)
nogo_resid = residuals.lm(fl_looking_nogo)

fl_looking_correct_looks_but = lm(prop_correct_looks_but_z_score ~ composite_congruency_effect + composite_switch_effect + age_months_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl)
correct_looks_but_resid = residuals.lm(fl_looking_correct_looks_but)

nogo_but_resid = data.frame(nogo_resid, correct_looks_but_resid)
```

Plot these residuals to get the relationship between switch RT cost and correct points on but trials:
```{r}
ggplot(data = nogo_but_resid, aes(x = nogo_resid, y = correct_looks_but_resid)) +
  theme(text = element_text(size = 14)) +  
  geom_point() +
  geom_smooth(method="lm") +
  xlab('No-Go Cost') +
  ylab('Prop. looks to correct image on but trials') +
  ggtitle("'But' accuracy and No-Go Cost")

ggsave('resid_nogo_correct_but_non_outlier_looks.pdf', path = '../graphs', height = 4, width =6)
```

Plot raw data correlation to get the relationship between no go cost and correct looks on but trials:
```{r}
ggplot(data = prop_looks_correct_fl, aes(x = flanker_nogo_effect_z_score, y = prop_correct_looks_but_z_score)) +
  theme(text = element_text(size = 14)) +  
  geom_point() +
  geom_smooth(method="lm") +
  xlab('No-Go Cost') +
  ylab('Prop. looks to correct image on but trials') +
  ggtitle("'But' accuracy and No-Go Cost")

ggsave('corr_nogo_correct_but_non_outlier_looks.pdf', path = '../graphs', height = 4, width =6)
```


## Low vs. high Flanker cost children

As an exploratory analysis, we will separate children into those with low and high Flanker costs and visualize their eye gaze patterns to see if there are clear differences.

### No go cost

Separate by low/high no-go cost:
```{r}
full_flanker_df = full_flanker_df %>% mutate(low_high_nogo_cost = case_when(
  flanker_nogo_effect_z_score < 0 ~ 'Low no-go cost',
  flanker_nogo_effect_z_score > 0 ~ 'High no-go cost'
))
```

Make time sequence data with low/high no-go group:
```{r}
test_df_child = test_df %>% filter(child_adult_group == "children")
test_df_child = left_join(test_df_child, full_flanker_df, by = 'participant_number_fl')

timecourse_correct_point_nogo <- make_time_sequence_data(test_df_child, time_bin_size = 20, 
                                         predictor_columns = c("condition",
                                                               "correct_point",
                                                               "low_high_nogo_cost"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number.x") %>%
  filter(!is.na(low_high_nogo_cost))

```

Make time course graph for high vs. low no-go cost and correct vs. incorrect points:
```{r}
plot(timecourse_correct_point_nogo, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_grid(rows = vars(correct_point), cols = vars(low_high_nogo_cost)) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image: High vs. low no-go cost")

ggsave('timecourse_nogo_high_low.pdf', path = '../graphs', height = 5, width = 9)
```

## Low/high switch RT difference

Separate by low/high switch RT:
```{r}
test_df_child = test_df_child %>% mutate(low_high_switch_rt_diff = case_when(
  flanker_switch_rt_z_score < 0 ~ 'Low switch RT cost',
  flanker_switch_rt_z_score > 0 ~ 'High switch RT cost'
))
```

Make time sequence data with low/high switch RT difference group:
```{r}
timecourse_correct_point_switch_rt <- make_time_sequence_data(test_df_child, time_bin_size = 20, 
                                         predictor_columns = c("condition",
                                                               "correct_point",
                                                               "low_high_switch_rt_diff"),
                                         aois = c("AVERAGE_IA_1_SAMPLE_COUNT_."),
                                         summarize_by = "participant_number.x") %>%
  filter(!is.na(low_high_switch_rt_diff))

```

Make time course graph for high vs. low switch RT cost and correct vs. incorrect points:
```{r}
plot(timecourse_correct_point_switch_rt, predictor_column = "condition") + theme_bw() +  
  theme(text = element_text(size = 12)) +  
  geom_hline(yintercept=0.5, colour="black",size=I(0.5),show.legend = FALSE)+
  geom_vline(xintercept=0, colour="black",size=I(0.5),show.legend = FALSE) +
  ylim(0,1) +
  xlim(-1000, 4000) +
  facet_grid(rows = vars(correct_point), cols = vars(low_high_switch_rt_diff)) +
  xlab("Time since connective onset (ms)") +
  ylab("Proportion of looks to semantically associated image") +
  ggtitle("Proportion of looks to semantically associated image: High vs. low switch RT cost")

ggsave('timecourse_switch_rt_high_low.pdf', path = '../graphs', height = 5, width = 9)
```


# SES analysis

Import anonymized SES dataframe:
```{r}
ses_df = read.csv('../data/ses_df_nonidentifiable.csv')
ses_df = ses_df %>% select(-X)
```

## SES and pointing responses


Merge SES data with pointing dataframe:
```{r}
pointing_df_partic_cond_ses = left_join(pointing_df_partic_cond, ses_df)
pointing_df_partic_cond_ses = pointing_df_partic_cond_ses %>% 
  filter(!is.na(ses_index))
```

SES summary statistics:
```{r}
mean(na.omit(pointing_df_partic_cond_ses$educ_level_parent1))
median(na.omit(pointing_df_partic_cond_ses$educ_level_parent1))
min(na.omit(pointing_df_partic_cond_ses$educ_level_parent1))
max(na.omit(pointing_df_partic_cond_ses$educ_level_parent1))
```

Run regression for prop of correct points with SES as predictor:
```{r}
fl_pointing_ses_lm = lm(prop_correct_points_but_z_score ~ composite_congruency_effect + composite_switch_effect + flanker_nogo_effect_z_score + age_months_z_score + educ_level_parent1_z_score + prop_correct_points_so_z_score, 
                    data = pointing_df_partic_cond_ses)
summary(fl_pointing_ses_lm)

vif(fl_pointing_ses_lm)
```

Run regression without combining RT and acc z-scores:
```{r}
fl_pointing_ses_separate_lm = lm(prop_correct_points_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score +  flanker_nogo_effect_z_score + age_months_z_score + educ_level_parent1_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond_ses)
summary(fl_pointing_ses_separate_lm)

vif(fl_pointing_ses_separate_lm)
```

## SES and proportion of looks

Merge prop looks data with SES data:
```{r}
prop_looks_correct_fl_ses = left_join(prop_looks_correct_fl, ses_df)
prop_looks_correct_fl_ses = prop_looks_correct_fl_ses %>% 
  filter(!is.na(ses_index))
```

We have a few outliers with high no-go cost, so exclude them from the model:
```{r}
full_flanker_df$participant_number[full_flanker_df$flanker_nogo_effect_z_score > 3]
prop_looks_correct_fl_ses_non_outlier = prop_looks_correct_fl_ses %>% filter(! participant_number %in% c(20032308, 29032301, 3042306))
```

Run regression with SES
```{r}
fl_looking_ses_non_outlier_lm = lm(prop_correct_looks_but_z_score ~ composite_congruency_effect + composite_switch_effect + flanker_nogo_effect_z_score + age_months_z_score + educ_level_parent1 + prop_correct_looks_so_z_score, data = prop_looks_correct_fl_ses_non_outlier)
summary(fl_looking_ses_non_outlier_lm)

vif(fl_looking_ses_non_outlier_lm)
```

Run regression with SES and separate accuracy and RT costs:
```{r}
fl_looking_ses_non_outlier_separate_lm = lm(prop_correct_looks_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score + flanker_nogo_effect_z_score + age_months_z_score + educ_level_parent1 + prop_correct_looks_so_z_score, data = prop_looks_correct_fl_ses_non_outlier)
summary(fl_looking_ses_non_outlier_separate_lm)

vif(fl_looking_ses_non_outlier_separate_lm)
```

To plot relationship between no-go and looks to correct image on but trials, create versions of the regression predicting each outcome and get the residuals:
```{r}
fl_no_go = lm(flanker_nogo_effect_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score +  age_months_z_score + educ_level_parent1_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl_ses)
fl_no_go_resid = residuals.lm(fl_no_go)

fl_correct_looks_but = lm(prop_correct_looks_but_z_score ~ flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_acc_z_score +  age_months_z_score + educ_level_parent1_z_score + prop_correct_looks_so_z_score, 
                             data = prop_looks_correct_fl_ses)
correct_looks_but_resid = residuals.lm(fl_correct_looks_but)

nogo_looks_but_resid = data.frame(fl_no_go_resid, correct_looks_but_resid)
```

Plot these residuals to get the relationship between no go cost and correct looks on but trials:
```{r}
ggplot(data = nogo_looks_but_resid, aes(x = fl_no_go_resid, y = correct_looks_but_resid)) +
  theme(text = element_text(size = 14)) +  
  geom_point() +
  geom_smooth(method="lm") +
  xlab('Flanker no-go cost') +
  ylab('Prop. looks to correct image on but trials') +
  ggtitle("") +
  theme(plot.margin=unit(c(1,1,1,1), "cm"))

ggsave('resid_nogo_correct_but_looks.pdf', path = '../graphs', height = 4, width =6)

# this is to save the plot so a combined plot with the SES effect can be put together later:

# nogo_looks = ggplot(data = nogo_looks_but_resid, aes(x = fl_no_go_resid, y = correct_looks_but_resid)) +
#   theme(text = element_text(size = 14)) +  
#   geom_point() +
#   geom_smooth(method="lm") +
#   xlab('Flanker no-go cost') +
#   ylab('Prop. looks to correct image on but trials') +
#   ggtitle("") +
#   theme(plot.margin=unit(c(1,1,1,1), "cm"))
```

To plot relationship between SES and points to correct image on but trials, create versions of the regression predicting each outcome and get the residuals:
```{r}
fl_ses = lm(educ_level_parent1_z_score ~ flanker_nogo_effect_z_score + flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_rt_z_score + flanker_switch_acc_z_score +  age_months_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond_ses)
fl_ses_resid = residuals.lm(fl_ses)

fl_correct_points_but = lm(prop_correct_points_but_z_score ~ flanker_nogo_effect_z_score + flanker_congruency_rt_z_score + flanker_congruency_acc_z_score + flanker_switch_acc_z_score + flanker_switch_rt_z_score + age_months_z_score + prop_correct_points_so_z_score, 
                             data = pointing_df_partic_cond_ses, subset = !is.na(educ_level_parent1_z_score))
correct_points_but_resid = residuals.lm(fl_correct_points_but)

ses_points_but_resid = data.frame(fl_ses_resid, correct_points_but_resid)
```

Plot these residuals to get the relationship between SES and correct points on but trials:
```{r}
ggplot(data = ses_points_but_resid, aes(x = fl_ses_resid, y = correct_points_but_resid)) +
  theme(text = element_text(size = 14)) +  
  geom_point() +
  geom_smooth(method="lm") +
  xlab('Maternal education level') +
  ylab('Prop. points to correct image on but trials') +
  ggtitle("") +
  theme(plot.margin=unit(c(1,1,1,1), "cm"))

ggsave('resid_ses_correct_but_points.pdf', path = '../graphs', height = 4, width =6)

# this is to save the plot so a combined plot with the no go effect can be put together later:

# ses_points = ggplot(data = ses_points_but_resid, aes(x = fl_ses_resid, y = correct_points_but_resid)) +
#   theme(text = element_text(size = 14)) +  
#   geom_point() +
#   geom_smooth(method="lm") +
#   xlab('Maternal education level') +
#   ylab('Prop. points to correct image on but trials') +
#   ggtitle("") +
#   theme(plot.margin=unit(c(1,1,1,1), "cm"))
```

Combined plot with no-go cost/looks and SES/points (only run this is you uncomment the code above to save the individual plots):
```{r}
# grid.arrange(nogo_looks, ses_points, nrow=1)
# 
# nogo_ses_residuals = arrangeGrob(nogo_looks, ses_points, nrow=1)
#  ggsave(file="nogo_ses_residuals.pdf", path = '../graphs', nogo_ses_residuals)
#  
#  nogo_ses_residuals = arrangeGrob(nogo_looks, ses_points, nrow=1)
#  ggsave(file="nogo_ses_residuals.jpg", path = '../graphs', nogo_ses_residuals)
```

