---
title: "Flanker cost calculation"
author: "Elizabeth Swanson"
date: "2023-05-04"
output: html_document
---

# Set-up

Load required packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(eyetrackingR)
library(lme4)
library(readxl)
library(lmerTest)
source("helpers.R")
theme_set(theme_bw())
```

# Loading data

Load Flanker data files:
```{r}
flanker_df = read.csv('../data/flanker_df.csv')
participant_df = read_excel('../data/participant-log-connectives-cog-control.xlsx')
participant_df = participant_df %>% type.convert(as.is = TRUE)
```

Rename age groups:
```{r}
participant_df = participant_df %>% mutate(age_group = case_when(
  age_group == '4' ~ '4-year-olds',
  age_group == '5' ~ '5-year-olds',
  age_group == '6' ~ '6-year-olds',
  age_group == 'adult' ~ 'adults'
))
```


### Flanker data prep

Enter switch data as either 'switch' or 'non-switch':
```{r}
flanker_df = flanker_df %>% 
  mutate(switch = case_when(
    switch == 0 ~ 'nonswitch',
    switch == 1 ~ 'switch'))
```

Exclude participants who we do not have sufficient trials to analyze data from:
```{r}
flanker_df = flanker_df %>% filter(participant_number_fl != 33003236, participant_number_fl != 220323042, participant_number_fl != 2103230301)
```

#### Reaction time

Pull out data from the test block, in conditions other than no-go, where participant answered correctly (as we are looking at RT):
```{r}
flanker_df_rt = flanker_df %>% filter(block == 'test', correct == 1, condition != 'nogo')
```

Calculate each participant's mean RT and sd:
```{r}
flanker_df_rt = flanker_df_rt %>% group_by(participant_number_fl) %>% 
  mutate(partic_mean_rt = mean(rt), 
         partic_sd_rt = sd(rt),
         partic_max_rt = partic_mean_rt + 3*partic_sd_rt,
         partic_min_rt = partic_mean_rt - 3*partic_sd_rt)
```

If participant's RT is more than 3 SDs above or below the mean, replace it with that number:
```{r}
flanker_df_rt = flanker_df_rt %>% mutate(clean_rt = ifelse(rt==-1, -1,
                           ifelse(rt >= partic_max_rt, partic_max_rt,
                                  ifelse(rt <= partic_min_rt, partic_min_rt, rt))))
```

How many RTs were replaced?
```{r}
flanker_df_rt %>% filter(clean_rt != rt) %>% length()
```

#### Accuracy

Pull out trials from test block:
```{r}
flanker_df_acc = flanker_df %>% filter(block == 'test')
```


### Congruency effect


#### Congruency effect on reaction time

Calculate each participant's mean RT for congruent and incongruent conditions:
```{r}
flanker_df_rt_congruent = flanker_df_rt %>% group_by(participant_number_fl, condition) %>% 
  summarise(partic_cond_mean_rt = mean(clean_rt))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  spread(key = 'condition', value = 'partic_cond_mean_rt') %>%
  rename(congruent_mean_rt = congruent, incongruent_mean_rt = incongruent)
```

Test whether there is a significant difference in RT by condition (congruent vs. incongruent):
```{r}
t.test(flanker_df_rt_congruent$incongruent_mean_rt, flanker_df_rt_congruent$congruent_mean_rt, paired=TRUE)
```
Children had significantly lower RTs in the congruent condition than the incongruent condition.

Calculate the congruency effect on RT for each participant:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  mutate(congruency_effect_rt = incongruent_mean_rt - congruent_mean_rt)
```

Add overall mean and SD of congruency effect on RT:
```{r}
flanker_df_rt_congruent$overall_mean_congruency_rt = 
  mean(flanker_df_rt_congruent$congruency_effect_rt)
flanker_df_rt_congruent$overall_sd_congruency_rt = 
  sd(flanker_df_rt_congruent$congruency_effect_rt)
```

Calculate congruency Z score for each participant for RT:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  mutate(flanker_congruency_rt_z_score = 
           ((congruency_effect_rt - overall_mean_congruency_rt)/overall_sd_congruency_rt))
```

#### Congruency effect on accuracy

Calculate each participant's accuracy and errors for congruent and incongruent conditions:
```{r}
flanker_df_acc_congruent = flanker_df_acc %>% group_by(participant_number_fl, condition) %>% 
  summarise(partic_cond_mean_acc = mean(correct),
            partic_cond_mean_errors = (1-partic_cond_mean_acc))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_acc_congruent = flanker_df_acc_congruent %>% 
  select(-partic_cond_mean_errors) %>% # we don't need errors if we're looking at accuracy
  spread(key = 'condition', value = 'partic_cond_mean_acc') %>%
  rename(congruent_mean_acc = congruent, incongruent_mean_acc = incongruent, 
         nogo_mean_acc = nogo)
```

T test to see if effect of condition (congruent vs. incongruent) on accuracy is significant:
```{r}
t.test(flanker_df_acc_congruent$congruent_mean_acc, flanker_df_acc_congruent$incongruent_mean_acc, paired=TRUE)
```
Children were significantly more accurate on congruent trials than incongruent trials.

Calculate the congruency effect on accuracy for each participant:
```{r}
flanker_df_acc_congruent = flanker_df_acc_congruent %>% 
  mutate(congruency_effect_acc = congruent_mean_acc - incongruent_mean_acc)
```

Calculate overall mean and SD of congruency effect on accuracy:
```{r}
flanker_df_acc_congruent$overall_mean_congruency_acc = 
  mean(flanker_df_acc_congruent$congruency_effect_acc)
flanker_df_acc_congruent$overall_sd_congruency_acc = 
  sd(flanker_df_acc_congruent$congruency_effect_acc)
```

Calculate congruency Z score for each participant for accuracy:
```{r}
flanker_df_acc_congruent = flanker_df_acc_congruent %>% 
  mutate(flanker_congruency_acc_z_score = ((congruency_effect_acc - overall_mean_congruency_acc)/overall_sd_congruency_acc))
```

#### Composite congruency effect

Join RT and accuracy data sets:
```{r}
flanker_df_comp_congruent = full_join(flanker_df_rt_congruent, flanker_df_acc_congruent)
```

Calculate composite congruency effect for each participant:
```{r}
flanker_df_comp_congruent = flanker_df_comp_congruent %>%
  mutate(composite_congruency_effect = ((flanker_congruency_rt_z_score + flanker_congruency_acc_z_score)/2))
```


### Switch effect

#### Switch effect on reaction time

Calculate each participant's mean RT for switch and non-switch conditions:
```{r}
flanker_df_rt_switch = flanker_df_rt %>% 
  group_by(participant_number_fl, switch) %>% 
  summarise(partic_switch_mean_rt = mean(clean_rt)) %>%
  filter(!is.na(switch))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  spread(key = 'switch', value = 'partic_switch_mean_rt') %>%
  rename(switch_mean_rt = switch, nonswitch_mean_rt = nonswitch)
```

Test whether there is a significant difference in RT by switch type (switch vs. non-switch):
```{r}
t.test(flanker_df_rt_switch$switch_mean_rt, flanker_df_rt_switch$nonswitch_mean_rt, paired=TRUE)
```
Children had significantly lower RTs in non-switch trials than in switch trials.

Calculate the switch effect for each participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  mutate(switch_effect_rt = switch_mean_rt - nonswitch_mean_rt)
```

Look at overall mean and SD of switch effect for RT:
```{r}
flanker_df_rt_switch$overall_mean_switch_rt = 
  mean(flanker_df_rt_switch$switch_effect_rt)
flanker_df_rt_switch$overall_sd_switch_rt = 
  sd(flanker_df_rt_switch$switch_effect_rt)
```

Calculate switch Z score for each participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  mutate(flanker_switch_rt_z_score = ((switch_effect_rt - overall_mean_switch_rt)/overall_sd_switch_rt))
```

#### Switch effect on accuracy

Calculate each participant's accuracy for switch and non-switch conditions:
```{r}
flanker_df_acc_switch = flanker_df_acc %>% group_by(participant_number_fl, switch) %>% 
  summarise(partic_switch_mean_acc = mean(correct),
            partic_switch_mean_errors = (1-partic_switch_mean_acc))  %>%
  filter(!is.na(switch))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_acc_switch = flanker_df_acc_switch %>% 
  select(-partic_switch_mean_errors) %>% # we don't need errors if we're looking at accuracy
  spread(key = 'switch', value = 'partic_switch_mean_acc') %>%
  rename(switch_mean_acc = switch, nonswitch_mean_acc = nonswitch)
```

T test to see if effect of switch condition on accuracy is significant:
```{r}
t.test(flanker_df_acc_switch$nonswitch_mean_acc, flanker_df_acc_switch$switch_mean_acc, paired=TRUE)
```
There is not a significant difference in accuracy between switch and non-switch trials.

Calculate the switch effect on accuracy for each participant:
```{r}
flanker_df_acc_switch = flanker_df_acc_switch %>% 
  mutate(switch_effect_acc = nonswitch_mean_acc - switch_mean_acc)
```

Calculate overall mean and SD of switch effect on accuracy:
```{r}
flanker_df_acc_switch$overall_mean_switch_acc = 
  mean(flanker_df_acc_switch$switch_effect_acc)
flanker_df_acc_switch$overall_sd_switch_acc = 
  sd(flanker_df_acc_switch$switch_effect_acc)
```

Calculate switch Z score for each participant for accuracy:
```{r}
flanker_df_acc_switch = flanker_df_acc_switch %>% 
  mutate(flanker_switch_acc_z_score = ((switch_effect_acc - overall_mean_switch_acc)/overall_sd_switch_acc))
```

#### Composite switch effect

Join RT and accuracy data sets:
```{r}
flanker_df_comp_switch = full_join(flanker_df_rt_switch, flanker_df_acc_switch)
```

Calculate composite switch effect for each participant:
```{r}
flanker_df_comp_switch = flanker_df_comp_switch %>%
  mutate(composite_switch_effect = ((flanker_switch_rt_z_score + flanker_switch_acc_z_score)/2))
```


### Go-nogo cost

Pull out trials from test block and create column saying whether trial was go or no-go:
```{r}
flanker_df_nogo = flanker_df %>% filter(block == 'test') %>% 
  mutate(go_nogo = case_when(
    condition == 'congruent' ~ 'go',
    condition == 'incongruent' ~ 'go',
    condition == 'nogo' ~ 'nogo'
  ))
```

Add column marking whether child omitted response:
```{r}
flanker_df_nogo = flanker_df_nogo %>% mutate(omission = case_when(
  is.na(response) ~ TRUE,
  TRUE ~ FALSE
))
```

Calculate proportion of omissions on go vs. no-go trials:
```{r}
flanker_df_omit_nogo = flanker_df_nogo %>% group_by(participant_number_fl, go_nogo) %>%
  summarise(partic_gonogo_mean_omit = mean(omission),
            partic_gonogo_mean_response = 1-partic_gonogo_mean_omit)
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_omit_nogo = flanker_df_omit_nogo %>% 
  select(-partic_gonogo_mean_response) %>%
  spread(key = 'go_nogo', value = 'partic_gonogo_mean_omit') %>%
  rename(go_mean_omit = go, nogo_mean_omit = nogo)
```

T test to see if effect of go/no-go condition on omissions is significant:
```{r}
t.test(flanker_df_omit_nogo$go_mean_omit, flanker_df_omit_nogo$nogo_mean_omit, paired=TRUE)
```
There is a significant difference in omissions between go and no-go trials.

Calculate the switch effect on accuracy for each participant:
```{r}
flanker_df_omit_nogo = flanker_df_omit_nogo %>% 
  mutate(nogo_effect = go_mean_omit - nogo_mean_omit)
```

Calculate overall mean and SD of go/no-go effect on accuracy:
```{r}
flanker_df_omit_nogo$overall_mean_nogo_effect = 
  mean(flanker_df_omit_nogo$nogo_effect)
flanker_df_omit_nogo$overall_sd_nogo_effect = 
  sd(flanker_df_omit_nogo$nogo_effect)
```

Calculate go/no-go Z score for each participant for accuracy:
```{r}
flanker_df_omit_nogo = flanker_df_omit_nogo %>% 
  mutate(flanker_nogo_effect_z_score = ((nogo_effect - overall_mean_nogo_effect)/overall_sd_nogo_effect))
```

### Combining data sets for all Flanker costs

Combine all three datasets
```{r}
full_flanker_df = full_join(flanker_df_comp_congruent, flanker_df_comp_switch)
full_flanker_df = full_join(full_flanker_df, flanker_df_omit_nogo)
full_flanker_df = left_join(full_flanker_df, participant_df)
```

Calculate Z score for age in months:
```{r}
full_flanker_df$mean_age_months = mean(full_flanker_df$age_months)
full_flanker_df$sd_age_months = sd(full_flanker_df$age_months)
full_flanker_df = full_flanker_df %>% 
  mutate(age_months_z_score = (age_months - mean_age_months)/sd_age_months)
```

Write full Flanker cost data to a csv for analysis:
```{r}
write.csv(full_flanker_df, '../data/full_flanker_df.csv')
```


```{r}
flanker_df_acc_overall = flanker_df %>% filter(condition == 'congruent' | condition == 'incongruent') %>% group_by(participant_number_fl) %>% mutate(partic_mean_acc_go = mean(correct)) %>%
  group_by(participant_number_fl) %>% filter(row_number() == 1)
flanker_df_acc_overall = left_join(flanker_df_acc_overall, flanker_df_omit_nogo)
cor(na.omit(flanker_df_acc_overall$partic_mean_acc_go), na.omit(flanker_df_acc_overall$nogo_effect))
```










Incorrect way of doing no-go cost??

Calculate accuracy by trial type (go vs. no-go):
```{r}
flanker_df_acc_nogo = flanker_df_nogo %>% group_by(participant_number_fl, go_nogo) %>% 
  summarise(partic_go_nogo_mean_acc = mean(correct))
```

Reshape data set to wide format so there is one row per participant, and add errors column:
```{r}
flanker_df_acc_nogo = flanker_df_acc_nogo %>% 
  spread(key = 'go_nogo', value = 'partic_go_nogo_mean_acc') %>%
  rename(go_mean_acc = go, nogo_mean_acc = nogo) %>%
  mutate(go_mean_errors = 1-go_mean_acc,
         nogo_mean_errors = 1-nogo_mean_acc)
```

T test to see if effect of go/no-go condition on accuracy is significant:
```{r}
t.test(flanker_df_acc_nogo$go_mean_acc, flanker_df_acc_nogo$nogo_mean_acc, paired=TRUE)
```
There is not a significant difference between the go and no-go conditions.

Calculate the no-go cost on accuracy for each participant:
```{r}
flanker_df_acc_nogo = flanker_df_acc_nogo %>% 
  mutate(nogo_effect = nogo_mean_errors - go_mean_acc)
```



