---
title: "Flanker cost calculation"
author: "Elizabeth Swanson"
date: "2023-05-04"
output: html_document
---

# Set-up

Load required packages:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(eyetrackingR)
library(lme4)
library(readxl)
library(lmerTest)
source("helpers.R")
theme_set(theme_bw())
```

# Loading data

Load Flanker data files:
```{r}
flanker_df = read.csv('../data/flanker_df.csv')
participant_df = read_excel('../data/participant-log-connectives-cog-control.xlsx')
participant_df = participant_df %>% type.convert(as.is = TRUE)
```

Rename age groups:
```{r}
participant_df = participant_df %>% mutate(age_group = case_when(
  age_group == '4' ~ '4-year-olds',
  age_group == '5' ~ '5-year-olds',
  age_group == '6' ~ '6-year-olds',
  age_group == 'adult' ~ 'adults'
))
```


### Flanker data prep

Enter switch data as either 'switch' or 'non-switch':
```{r}
flanker_df = flanker_df %>% 
  mutate(switch = case_when(
    switch == 0 ~ 'nonswitch',
    switch == 1 ~ 'switch'))
```

Exclude participants who we do not have sufficient trials to analyze data from:
```{r}
flanker_df = flanker_df %>% filter(participant_number_fl != 33003236, participant_number_fl != 220323042, participant_number_fl != 2103230301)
```

#### Reaction time

Pull out data from the test block, in conditions other than no-go, where participant answered correctly (as we are looking at RT):
```{r}
flanker_df_rt = flanker_df %>% filter(block == 'test', correct == 1, condition != 'nogo')
```

Calculate each participant's mean RT and sd:
```{r}
flanker_df_rt = flanker_df_rt %>% group_by(participant_number_fl) %>% 
  mutate(partic_mean_rt = mean(rt), 
         partic_sd_rt = sd(rt),
         partic_max_rt = partic_mean_rt + 3*partic_sd_rt,
         partic_min_rt = partic_mean_rt - 3*partic_sd_rt)
```

If participant's RT is more than 3 SDs above or below the mean, replace it with that number:
```{r}
flanker_df_rt = flanker_df_rt %>% mutate(clean_rt = ifelse(rt==-1, -1,
                           ifelse(rt >= partic_max_rt, partic_max_rt,
                                  ifelse(rt <= partic_min_rt, partic_min_rt, rt))))
```

How many RTs were replaced?
```{r}
flanker_df_rt %>% filter(clean_rt != rt) %>% length()
```

#### Accuracy

Pull out trials from test block:
```{r}
flanker_df_acc = flanker_df %>% filter(block == 'test')
```


### Congruency effect


#### Congruency effect on reaction time

Calculate each participant's mean RT for congruent and incongruent conditions:
```{r}
flanker_df_rt_congruent = flanker_df_rt %>% group_by(participant_number_fl, condition) %>% 
  summarise(partic_cond_mean_rt = mean(clean_rt))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  spread(key = 'condition', value = 'partic_cond_mean_rt') %>%
  rename(congruent_mean_rt = congruent, incongruent_mean_rt = incongruent)
```

Test whether there is a significant difference in RT by condition (congruent vs. incongruent):
```{r}
t.test(flanker_df_rt_congruent$incongruent_mean_rt, flanker_df_rt_congruent$congruent_mean_rt, paired=TRUE)
```

Calculate the congruency effect on RT for each participant:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  mutate(congruency_effect_rt = incongruent_mean_rt - congruent_mean_rt)
```

Add overall mean and SD of congruency effect on RT:
```{r}
flanker_df_rt_congruent$overall_mean_congruency_rt = 
  mean(flanker_df_rt_congruent$congruency_effect_rt)
flanker_df_rt_congruent$overall_sd_congruency_rt = 
  sd(flanker_df_rt_congruent$congruency_effect_rt)
```

Calculate congruency Z score for each participant for RT:
```{r}
flanker_df_rt_congruent = flanker_df_rt_congruent %>% 
  mutate(flanker_congruency_rt_z_score = 
           ((congruency_effect_rt - overall_mean_congruency_rt)/overall_sd_congruency_rt))
```

#### Congruency effect on accuracy

Calculate each participant's accuracy and errors for congruent and incongruent conditions:
```{r}
flanker_df_acc_congruent = flanker_df_acc %>% group_by(participant_number_fl, condition) %>% 
  summarise(partic_cond_mean_acc = mean(correct),
            partic_cond_mean_errors = (1-partic_cond_mean_acc))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_errors_congruent = flanker_df_acc_congruent %>% 
  select(-partic_cond_mean_acc) %>%
  spread(key = 'condition', value = 'partic_cond_mean_errors') %>%
  rename(congruent_mean_errors = congruent, incongruent_mean_errors = incongruent, 
         nogo_mean_errors = nogo)
```

T test to see if effect of condition (congruent vs. incongruent) on accuracy is significant:
```{r}
t.test(flanker_df_errors_congruent$incongruent_mean_errors, flanker_df_errors_congruent$congruent_mean_errors, paired=TRUE)
```

Calculate the congruency effect on accuracy for each participant:
```{r}
flanker_df_errors_congruent = flanker_df_errors_congruent %>% 
  mutate(congruency_effect_errors = incongruent_mean_errors - congruent_mean_errors)
```

Calculate overall mean and SD of congruency effect on accuracy:
```{r}
flanker_df_errors_congruent$overall_mean_congruency_errors = 
  mean(flanker_df_errors_congruent$congruency_effect_errors)
flanker_df_errors_congruent$overall_sd_congruency_errors = 
  sd(flanker_df_errors_congruent$congruency_effect_errors)
```

Calculate congruency Z score for each participant for accuracy:
```{r}
flanker_df_errors_congruent = flanker_df_errors_congruent %>% 
  mutate(flanker_congruency_errors_z_score = ((congruency_effect_errors - overall_mean_congruency_errors)/overall_sd_congruency_errors))
```

#### Composite congruency effect

Join RT and accuracy data sets:
```{r}
flanker_df_comp_congruent = full_join(flanker_df_rt_congruent, flanker_df_errors_congruent)
```

Calculate composite congruency effect for each participant:
```{r}
flanker_df_comp_congruent = flanker_df_comp_congruent %>%
  mutate(composite_congruency_effect = ((flanker_congruency_rt_z_score + flanker_congruency_errors_z_score)/2))
```


### Switch effect

#### Switch effect on reaction time

Calculate each participant's mean RT for switch and non-switch conditions:
```{r}
flanker_df_rt_switch = flanker_df_rt %>% 
  group_by(participant_number_fl, switch) %>% 
  summarise(partic_switch_mean_rt = mean(clean_rt)) %>%
  filter(!is.na(switch))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  spread(key = 'switch', value = 'partic_switch_mean_rt') %>%
  rename(switch_mean_rt = switch, nonswitch_mean_rt = nonswitch)
```

Test whether there is a significant difference in RT by switch type (switch vs. non-switch):
```{r}
t.test(flanker_df_rt_switch$switch_mean_rt, flanker_df_rt_switch$nonswitch_mean_rt, paired=TRUE)
```

Calculate the switch effect for each participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  mutate(switch_effect_rt = switch_mean_rt - nonswitch_mean_rt)
```

Look at overall mean and SD of switch effect:
```{r}
flanker_df_rt_switch$overall_mean_switch = 
  mean(flanker_df_rt_switch$switch_effect_rt)
flanker_df_rt_switch$overall_sd_switch = 
  sd(flanker_df_rt_switch$switch_effect_rt)
```

Calculate switch Z score for each participant:
```{r}
flanker_df_rt_switch = flanker_df_rt_switch %>% 
  mutate(flanker_switch_rt_z_score = ((switch_effect_rt - overall_mean_switch)/overall_sd_switch))
```

#### Switch effect on accuracy

Calculate each participant's accuracy for switch and non-switch conditions:
```{r}
flanker_df_acc_switch = flanker_df_acc %>% group_by(participant_number_fl, switch) %>% 
  summarise(partic_switch_mean_acc = mean(correct),
            partic_switch_mean_errors = (1-partic_switch_mean_acc))  %>%
  filter(!is.na(switch))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_errors_switch = flanker_df_acc_switch %>% 
  select(-partic_switch_mean_acc) %>%
  spread(key = 'switch', value = 'partic_switch_mean_errors') %>%
  rename(switch_mean_errors = switch, nonswitch_mean_errors = nonswitch)
```

T test to see if effect of switch condition on accuracy is significant:
```{r}
t.test(flanker_df_errors_switch$switch_mean_errors, flanker_df_errors_switch$nonswitch_mean_errors, paired=TRUE)
```

Calculate the switch effect on accuracy for each participant:
```{r}
flanker_df_errors_switch = flanker_df_errors_switch %>% 
  mutate(switch_effect_errors = switch_mean_errors - nonswitch_mean_errors)
```

Calculate overall mean and SD of switch effect on accuracy:
```{r}
flanker_df_errors_switch$overall_mean_switch_errors = 
  mean(flanker_df_errors_switch$switch_effect_errors)
flanker_df_errors_switch$overall_sd_switch_errors = 
  sd(flanker_df_errors_switch$switch_effect_errors)
```

Calculate switch Z score for each participant for accuracy:
```{r}
flanker_df_errors_switch = flanker_df_errors_switch %>% 
  mutate(flanker_switch_errors_z_score = ((switch_effect_errors - overall_mean_switch_errors)/overall_sd_switch_errors))
```

#### Composite switch effect

Join RT and accuracy data sets:
```{r}
flanker_df_comp_switch = full_join(flanker_df_rt_switch, flanker_df_errors_switch)
```

Calculate composite switch effect for each participant:
```{r}
flanker_df_comp_switch = flanker_df_comp_switch %>%
  mutate(composite_switch_effect = ((flanker_switch_rt_z_score + flanker_switch_errors_z_score)/2))
```


### Go-nogo cost

Pull out trials from test block:
```{r}
flanker_df_nogo = flanker_df %>% filter(block == 'test')
```

Add a column to say if participant didn't respond:
```{r}
flanker_df_nogo = flanker_df_nogo %>% mutate(omission = ifelse(is.na(response), 1, 0))
```

Summarize number of omissions by condition:
```{r}
flanker_df_nogo = flanker_df_nogo %>% 
  group_by(participant_number_fl, condition) %>% 
  summarise(partic_cond_omit = sum(omission))
```

Reshape data set to wide format so there is one row per participant:
```{r}
flanker_df_nogo = flanker_df_nogo %>% 
  spread(key = 'condition', value = 'partic_cond_omit') %>%
  rename(congruent_omit = congruent, incongruent_omit = incongruent, nogo_omit = nogo)
# 31032337 never omitted - exclude?
```

Calculate total omission errors on go and no-go trials:
```{r}
flanker_df_nogo = flanker_df_nogo %>% 
  mutate(omission_errors_go = congruent_omit + incongruent_omit)
```

Calculate no-go cost (omission errors on go trials minus correct omissions on no-go trials):
```{r}
flanker_df_nogo = flanker_df_nogo %>% 
  mutate(nogo_cost = omission_errors_go - nogo_omit)
# should this be done with proportions?
```

Calculate overall mean and SD of no-go cost:
```{r}
flanker_df_nogo$overall_mean_nogo_cost = 
  mean(flanker_df_nogo$nogo_cost)
flanker_df_nogo$overall_sd_nogo_cost = 
  sd(flanker_df_nogo$nogo_cost)
```

Calculate Z score for each participant for no-go cost:
```{r}
flanker_df_nogo = flanker_df_nogo %>% 
  mutate(nogo_cost_z_score = ((nogo_cost - overall_mean_nogo_cost)/overall_sd_nogo_cost))
```

### Combining data sets for all Flanker costs

Combine all three datasets
```{r}
full_flanker_df = full_join(flanker_df_comp_congruent, flanker_df_comp_switch)
full_flanker_df = full_join(full_flanker_df, flanker_df_nogo)
full_flanker_df = left_join(full_flanker_df, participant_df)
```

Calculate Z score for age in months:
```{r}
full_flanker_df$mean_age_months = mean(full_flanker_df$age_months)
full_flanker_df$sd_age_months = sd(full_flanker_df$age_months)
full_flanker_df = full_flanker_df %>% 
  mutate(age_months_z_score = (age_months - mean_age_months)/sd_age_months)
```

Write full Flanker cost data to a csv for analysis:
```{r}
write.csv(full_flanker_df, '../data/full_flanker_df.csv')
```


